---
title: "Adv_R(HW1)"
author: "Neha Singh 24218922"
format: 
  pdf:
    fontsize: 12pt
    mainfont: "Times New Roman"
execute:
  warning: false
  error: true
echo: false
---

## CO2 Uptake in Grass Plants

## Introduction

The `CO2` dataset records ***carbon dioxide uptake*** in grass plants.\
It helps us analyze plant response to changes in **CO₂ concentration**.

## Plot and Approach

We use the `ggplot2` package to create a scatter plot of **CO₂ concentration (conc)** against **uptake**, grouped by plant type.

```{r}
# Load the ggplot2 package for plotting
library(ggplot2)

# Create a scatter plot of CO2 concentration vs uptake
# Color the points by plant Type (Quebec or Mississippi)
ggplot(CO2, aes(x = conc, y = uptake, color = Type)) +
  geom_point() +  # Plot the individual observations
  geom_smooth(method = "lm", se = FALSE) +  # Add regression line without confidence interval
  labs(
    title = "CO2 Uptake vs Concentration in Grass Plants",  # Main title
    x = "CO2 Concentration (mL/L)",                         # X-axis label
    y = "CO2 Uptake (μmol/m² sec)"                          # Y-axis label
  ) +
  theme_minimal()  # Apply a clean minimal theme
```

## Description of the Graph

The plot illustrates the relationship between **`CO₂ concentration`** and **`uptake`** in grass plants.

A fitted linear model is shown for each plant group ***(Quebec and Mississippi)*** to visualize trends.\
Uptake generally increases with higher CO₂ concentration, with Quebec plants typically showing higher uptake under chilled conditions.

```{r}
# Update for second commit – edited June 16
```
